---
title: "5.4 Residual diagnostics"
output: html_document
date: '2022-04-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp3)
```

#### Example: Forecasting Google daily closing stock prices

```{r}
# Re-index based on trading days
google_stock <- gafa_stock %>%
  filter(Symbol == "GOOG", year(Date) >= 2015) %>%
  mutate(day = row_number()) %>%
  update_tsibble(index = day, regular = TRUE)

# Filter the year of interest
google_2015 <- google_stock %>% filter(year(Date) == 2015)
```

```{r}
autoplot(google_2015, Close) +
  labs(y = "$US",
       title = "Google daily closing stock prices in 2015")

```

```{r}
aug <- google_2015 %>%
  model(NAIVE(Close)) %>%
  augment()

autoplot(aug, .innov) +
  labs(y = "$US",
       title = "Residuals form the naive method")

```


```{r}
aug %>%
  ggplot(aes(x = .innov)) +
  geom_histogram() +
  labs(title = "Histogram of residuals")

```


```{r}
aug %>%
  ACF(.innov) %>%
  autoplot() +
  labs(title = "Residulas from the naive method")

```


```{r}
google_2015 %>%
  model(NAIVE(Close)) %>%
  gg_tsresiduals()
```

#### Portmanteau tests for autocorrelation

```{r}
aug %>% features(.innov, box_pierce, lag = 10, dof = 0)

```
bp_stat is not significant. 
Therefore, the hypothesis that the residual series is white noise does not rejected.

```{r}
aug %>% features(.innov, ljung_box, lag = 10, dof = 0)

```
bp_stat is not significant. 
Therefore, the hypothesis that the residual series is white noise does not rejected.


#### Portmanteau tests for the drift model

```{r}
fit <- google_2015 %>% model(RW(Close ~ drift()))
tidy(fit)
```


```{r}
augment(fit) %>% features(.innov, ljung_box, lag=10, dof=1)

```
bp_stat is not significant. 
Therefore, the hypothesis that the residual series is white noise does not rejected.

