---
title: "5.8 Evaluating point forecast accuracy"
output: html_document
date: '2022-04-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Training and test sets

#### Functions to subset a time series

```{r}
# Unique year contained original series
unique(year(aus_production$Quarter))
```



```{r}
# filter data since 1995 by filter function
aus_production %>%
  filter(year(Quarter) >= 1995) %>%
  pull(Quarter) %>%
  year()

```


```{r}
# filter data since 1995 Q1 by filter_index function
aus_production %>%
  filter_index("1995 Q1" ~ .) %>%
  pull(Quarter)
```


```{r}
# Extract the las 20 obs by slice function
aus_production %>%
  slice(n()-19:0)
```


```{r}
# Subset observations from groups
aus_retail %>%
  group_by(State, Industry) %>%
  slice(1:12)
```

#### Forecast errors

$$
e_{T+h} = y_{T+h} - \hat{y}_{T+h|T}
$$


- Residual
  - Calculated on training set
  - one-step forecast
- Forecast errors
  - Calculated on test set
  - Involve multi-step forecast


#### Scale-dependent errors
- Can not be used to compare series with different scales

- MAE: Mean Absolute Error
  - $ MAE = mean(|e_t|)$
- RMSE: Root Mean Squared error
  - $ RMSE = \sqrt{mean(e_t^2)}$

- Minimising the MAE will lead to forecasts of **the median**
- Minimising the RMSE will lead to forecasts of **the mean**
- Consequently, the RMSE is also widely used, despite being more difficult to interpret.


#### Percentage errors

- MAPE: Mean absolute percentage error
  - $ MAPE = mean(|p_t|),\, p_t = 100 * \frac{e_t}{y_t} $
  - Disadvantage
    - $p_t$ is infinite or undefined if $y_t$ = 0
    - $p_t$ takes extreme values if $y_t$ is close to zero
    - ex) temperatures can take 0 and negative values
- sMAPE: symmetric MAPE
  - $ sMAPE = mean(200*|y_t - \hat{y_t}|/(y_t + \hat{y_t})) $
  
  
#### Scaled errors
- Can compare series with diffrent time series
- Overcome the disadvantage of MAPE and sMAPE
- scaled error for non-seasonal time series 
$$
q_j = \frac{e_j}{\frac{1}{T-1}\sum^{T}_{t=2}|y_t-y_{t-1}|}
$$
- scaled error for seasonal time series 
  - m is the seasonal period

$$
q_j = \frac{e_j}{\frac{1}{T-m}\sum^{T}_{t=m+1}|y_t-y_{t-m}|}
$$

- MASE: Mean Absolute Scaled Error
  - $ MASE = mean(|q_j|) $
- RMSSE: Root Mean Squared Scaled Error
  - $ RMSSE = \sqrt{mean(q_j^2)}$
  - $ q_j = \frac{e_j}{\frac{1}{T-m}\sum^{T}_{t=m+1}(y_t-y_{t-m})^2}$
  - set m = 1 if non-sesonal time series

#### Example

```{r}
recent_production <- aus_production %>%
  filter(year(Quarter) >= 1992)
beer_train <- recent_production %>%
  filter(year(Quarter) <= 2007)

beer_fit <- beer_train %>%
  model(
    Mean = MEAN(Beer),
    `Naïve` = NAIVE(Beer),
    `Seasonal naïve` = SNAIVE(Beer),
    Drift = RW(Beer ~ drift())
  )

beer_fc <- beer_fit %>%
  forecast(h = 10)

beer_fc %>%
  autoplot(
    aus_production %>% filter(year(Quarter) >= 1992),
    level = NULL
  ) +
  labs(
    y = "Megalitres",
    title = "Forecasts for quarterly beer production"
  ) +
  guides(colour = guide_legend(title = "Forecast"))

```
```{r}
accuracy(beer_fc, recent_production)
```
