---
title: "5.9 Evaluating distribution forecast accuracy"
output: html_document
date: '2022-04-07'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Re-index based on trading days
google_stock <- gafa_stock %>%
  filter(Symbol == "GOOG", year(Date) >= 2015) %>%
  mutate(day = row_number()) %>%
  update_tsibble(index = day, regular = TRUE)
# Filter the year of interest
google_2015 <- google_stock %>% filter(year(Date) == 2015)
# Fit the models
google_fit <- google_2015 %>%
  model(
    Mean = MEAN(Close),
    `Na誰ve` = NAIVE(Close),
    Drift = NAIVE(Close ~ drift())
  )
# Produce forecasts for the trading days in January 2016
google_jan_2016 <- google_stock %>%
  filter(yearmonth(Date) == yearmonth("2016 Jan"))
google_fc <- google_fit %>%
  forecast(new_data = google_jan_2016)
```


#### Quantile scores

$$
Q_{p,t} = \left\{\begin{array} {}
\displaystyle 2(1-p)(f_{p,t} - y_t), if\,\, y_t < f_{p,t} \\
2p(y_t - f_{p,t}), if y_t >= f_{p,t}
\end{array}\right.
$$
- the error $(y_t - f_{p,t})$
- If $y_t > f_{p,t} $, "$Q_{p,t}$ gives a heavier penalty when the observation is greater than the estimated quantile than when the observation is less than the estimated quantile. The reverse is true for"  


```{r}
google_fc %>%
  filter(.model == "Na誰ve") %>%
  autoplot(bind_rows(google_2015, google_jan_2016), level=80)+
  labs(y = "$US",
       title = "Google closing stock prices")
```


```{r}
google_fc %>%
  filter(.model == "Na誰ve", Date == "2016-01-04") %>%
  accuracy(google_stock, list(qs=quantile_score), probs=0.10)
```
#### Winkler Score

$$
W_{\alpha,t} = \left\{\begin{array}{}
\displaystyle 
(u_{\alpha,t} - l_{\alpha, t}) + \frac{2}{\alpha}(l_{\alpha,t} - y_t) \;\;\;\;\; if \;\; y_t < l_{\alpha,t} \\

(u_{\alpha,t} - l_{\alpha, t}) 
\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; if \;\; y_t \leq l_{\alpha,t} \leq u_{\alpha,t}\\

(u_{\alpha,t} - l_{\alpha, t}) + \frac{2}{\alpha}(y_t - u_{\alpha,t}) \;\;\;\;\; if \;\; y_t < l_{\alpha,t}


\end{array}\right.
$$
- $ 100(1 - \alpha) \% $ prediction interval at time $t$ is given by $ [l_{\alpha,t}, u_{\alpha, t}] $ 

- low scores are associated the narrow prediction intervals
- if the observation falls outside the interval, the penalty applies proportional to how far it outside the interval.


```{r}
google_fc %>%
  filter(.model == "Na誰ve", Date == "2016-01-04") %>%
  accuracy(google_stock, list(winkler = winkler_score), level = 80)
```

#### Scale-free comparisons using skill scores

```{r}
google_fc %>%
  accuracy(google_stock, list(skill = skill_score(CRPS)))

```

