---
title: "8.1 Simple exponential smoothing"
output: html_document
date: '2022-04-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp3)
```

-   Simple Exponential Smoothing (SES)
    -   Suitable for data with no clear trend and seasonal pattern.
    -   The smoothing parameter: alpha
    -   When alpha is small, more weight on observations from the more distant part.
    -   When alpha is large, more weight on the more recent observations.

$$ 
\hat{y}_{T+1|T} = \alpha y_T + \alpha(1-\alpha) y{T-1} \alpha(1-\alpha)^2 y_{T-2} + \dots, 
\\ \text{where $0\le \alpha \le 1$}
$$

```{r}
algeria_economy <- global_economy %>%
  filter(Country == "Algeria")
algeria_economy %>%
  autoplot(Exports) +
  labs(y = "% of GDP", title = "Exports: Algeria")
```

#### Weighted average form

The forrecast at time T +1 is equal to a weighted average between the recent observation \$y_T\$ and the previous forecast \$\\hat{y}\_{T\|T-1}\$:

$$
\hat{y}_{T+1 | T} = \alpha y_T + (1 - \alpha)\hat{y}_{T|T-1} \\
\text{for $ t = 1, \dots T $}
$$

As for \$ \\hat{y}\_{2\|1} \$

$$
\hat{y}_{2|1} = \alpha y_1 + (1 - \alpha)l_0 \\
\text{$l_0$ is the first fitted value, which have to estimate.}
$$

Weighted average form:

$$
\hat{y}_{T+1|T} = \sum_{j=0}^{T-1}{\alpha(1-\alpha)^jy_{T-j}} +(1-\alpha)^Tl_0
$$

#### Component form

$$
\text{Forecast equation} \;\; \hat{y}_{t+h|t} = l_t \\
\text{Smoothing equation} \;\; l_t = \alpha y_t + (1-\alpha)l_{t-1} \\
\text{where $l_t$ is the level (or the smoothed value)}
$$

#### Flat forecasts

-   All forecasts take the same value, equal to the last level component

$$
\hat{y}_{T+h|T} = \hat{y}_{T+1|T} = l_T\\
h = 2,3, \dots
$$

#### Optimization

-   Choose \$\\alpha\$ so that minimize SSE

### Example: Algerian exports

```{r}
# Estimate parameters
fit <- algeria_economy %>%
  model(ETS(Exports ~ error("A") + trend("N") + season("N")))

fc <- fit %>%
  forecast(h = 5)

fc %>%
  autoplot(algeria_economy) +
  geom_line(aes(y = .fitted), col="#D55E00",
            data = augment(fit)) +
  labs(y="% of GDP", 
       title="Exports: Algeria",
       subtitle="Simple exponential smoothing applied"
       ) +
  guides(colour = "none")
```
