---
title: "5.10 time-series cross-validation"
output: html_document
date: '2022-04-07'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp3)
```


#### Simple linear regression

$$
y_t = \beta_0 + \beta_1x + \varepsilon_t
$$


#### Example: US consumption expenditure

```{r}
head(us_change)

```

```{r}
us_change %>%
  pivot_longer(c(Consumption, Income), names_to = "Series") %>%
  autoplot(value) +
  labs(y = "% change",
       title = "Percentage changes in personal consumption\n expenditure and personal income for the US")

```

```{r}
us_change %>%
  ggplot(aes(x = Income, y = Consumption)) +
  labs(y = "Consumption (quarterly % change)",
       x = "Income (quarterly % change)") +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
```{r}
us_change %>%
  model(TSLM(Consumption ~ Income)) %>%
  report()
```


#### Multiple linear regression

$$
y_t = \beta_0 + \beta_1x + \beta_2x + \cdots+ \beta_kx + \varepsilon_t
$$
#### Example: US consumption expenditure

```{r}
us_change %>%
  select(-Consumption, -Income) %>%
  pivot_longer(-Quarter) %>%
  ggplot(aes(Quarter, value, colour = name)) +
  geom_line() +
  facet_grid(name ~ ., scales = "free_y") +
  guides(colour = "none") +
  labs(y="% change")
```
```{r}
us_change %>%
  GGally::ggpairs(columns = 2:6)
```
#### Assumptions

Assumptions about errors($ \varepsilon_1,\cdots,\varepsilon_1$)
- The mean of errors is zero. Otherwise the forecasts are systematically biased.
- Errors are not autocorrelated. Otherwise, there is more information in the data that can be exploited. 
- Errors are unrelated to the predictors. Otherwise, there would be more information that should be included in the systematic part of the model.
- Errors follow a normal distribution with constant variance. Otherwise, the prediction interval will not be accurate.
