---
title: "7.2 Least square estimation"
output: html_document
date: '2022-04-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp3)
```

- Choose the coefficients by minimising the sum of squared erros
$$
\sum_{t=1}^T\varepsilon_t^2 = \sum_{t=1}^T(y_t-\beta_0-\beta_{x_1,t}-\beta_{x_2,t} - \cdots - \beta_{x_k,t})
$$


#### Example: US consumption expenditure

```{r}
fit_consMR <- us_change %>%
  model(tslm = TSLM(Consumption ~ Income + Production +
                                    Unemployment + Savings))
report(fit_consMR)

```
#### Fitted values

```{r}
augment(fit_consMR) %>%
  ggplot(aes(x = Quarter)) +
  geom_line(aes(y = Consumption, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  labs(y = NULL,
    title = "Percent change in US consumption expenditure"
  ) +
  scale_colour_manual(values=c(Data="black",Fitted="#D55E00")) +
  guides(colour = guide_legend(title = NULL))

```


```{r}
augment(fit_consMR) %>%
  ggplot(aes(x = Consumption, y = .fitted)) +
  geom_point() +
  labs(
    y = "Fitted (predicted values)",
    x = "Data (actual values)",
    title = "Percent change in US consumption expenditure"
  ) +
  geom_abline(intercept = 0, slope = 1)
```


#### Goodness-of-fit

R squared
$$
R^2 = \frac{\sum\hat{y}_t-\bar{y}^2}{\sum(y_t - \bar{y})^2}
$$
#### Example: US consumption expenditure

#### Standard error of the regression

- Residual Standar Error
  - $k$ is the number of predictors in the model
  - divide by (T-k-1) because we estimate k+1 parameters(the intercept + the coefficients of each predictors)
  
$$
\hat{\sigma}_e = \sqrt{ \frac{1}{T-k-1} \sum_{t=1}^{T}{e_t^2}}
$$

