---
title: "7.3 Evaluating the regression model"
output: html_document
date: '2022-04-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp3)
```

- Properties of residuals
  - The average of residual is zero
  
$$
\sum_{t=1}^{T}e_t = 0 
$$
  - No correlation with any predictors

$$
\sum_{t=1}^{T}{x_{k,t}\,e_t} = 0 \;\; \forall k
$$
#### ACF plot of residuals

#### Histgram of residuals

```{r}
fit_consMR <- us_change %>%
  model(tslm = TSLM(Consumption ~ Income + Production +
                                    Unemployment + Savings))

fit_consMR %>% gg_tsresiduals()
```
- Heteroscedasticity in the innovation residual plot
- Spike at lag 7 on ACF plot, but its ACF is not so strong
- Right skewness on Histogram


```{r}
augment(fit_consMR) %>%
  features(.innov, ljung_box, lag = 10, dof = 5)
```

#### Residual plots against predictors
- Expect the residuals to be randomly scattered without any systematic pattern.
- If there is a pattern, "the relationship may be nonlinear and the model will need to be modified accordingly"

```{r}
us_change %>%
  left_join(residuals(fit_consMR), by = "Quarter") %>%
  pivot_longer(Income:Unemployment,
               names_to = "regressor", values_to = "x") %>%
  ggplot(aes(x = x, y = .resid)) +
  geom_point() +
  facet_wrap(. ~ regressor, scales = "free_x") +
  labs(y = "Residuals", x = "")
```

#### Residual plots against fitted values
- Expect the residuals show no pattern
- If there is a pattern, or heteroscedasticity, consider transformation of response variable such as logarithm and root transformation. 

```{r}
augment(fit_consMR) %>%
  ggplot(aes(x = .fitted, y = .resid)) +
  geom_point() + labs(x = "Fitted", y = "Residuals")
```

#### Outliers and influential observations

#### Spurious regression
- Two non-stationary time series
  - ex) two series with upward trend
- Regressing non-stationary time series can lead to spurious regressions.
- "Spurious regression appears to be reasonable short-term forecast, but will generally not continue to work into the feature."

```{r}
# Regress air-passengers in Australia by rice production in Guinea 
fit <- aus_airpassengers %>%
  filter(Year <= 2011) %>%
  left_join(guinea_rice, by = "Year") %>%
  model(TSLM(Passengers ~ Production))

report(fit)
fit %>% gg_tsresiduals()
```


