---
title: "7.4 Some useful predictors"
output: html_document
date: '2022-04-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp3)
```

#### Trend

$$
y_t = \beta_0 + \beta t + \varepsilon_T \\ 
\rm{where} \;\;\;t = 1, \dots,T
$$

#### Dummy variable
(no code)

#### Seasonal dummy variables
- Dummy variables associating seasonal effect of time-series
- ex) daily observations and weekly seasonal effect
    - => six dummy variable (7 weekday - 1 )

#### Example: Australian quarterly beer production

```{r}
recent_production <- aus_production %>%
  filter(year(Quarter) >= 1992)
recent_production %>%
  autoplot(Beer) +
  labs(y = "Megalitres",
       title = "Australian quarterly beer production")
```
- Regression model with a linear trend and quarterly dummy variables

$$
y_t = \beta_0 + \beta_{1}t + \beta_{2}d_{2,t} + \beta_{3}d_{3,t}+ \beta_{4}d_{4,t} + \varepsilon_t \\
\rm{where}\;\;\;d_{i,t} = 1 \;\; \rm{if} \;\; t \;\rm{is \;in\; quarter\; i\; and\; 0\; otherwise} 
$$

```{r}
fit_beer <- recent_production %>%
  model(TSLM(Beer ~ trend() + season()))

report(fit_beer)
```
```{r}
augment(fit_beer) %>%
  ggplot(aes(x = Quarter)) +
  geom_line(aes(y = Beer, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  scale_colour_manual(
    values = c(Data = "black", Fitted = "#D55E00")
  ) +
  labs(y = "Megalitres",
       title = "Australian quarterly beer production",
       subtitle = "Time plot of beer production and predicted beer production"
       ) +
  guides(colour = guide_legend(title = "Series"))
```

```{r}
augment(fit_beer) %>%
  ggplot(aes(x = Beer, y = .fitted,
             colour = factor(quarter(Quarter)))) +
  geom_point() +
  labs(y = "Fitted", x = "Actual values",
       title = "Australian quarterly beer production",
       subtitle = "Actual beer production plotted against predicted beer production") +
  geom_abline(intercept = 0, slope = 1) +
  guides(colour = guide_legend(title = "Quarter"))
```

#### Intervention variables
- Intervention
  - ex)
    - competitor activity
    - advertising expenditure
    - industrial action
- If the effect lasts one period, use "spike" variable
  - "spike" variable takes 1 at the intervention and 0 otherwise
- If the effect is immediate and permanent effect, it causes a level shift.Use "step" variable.
  - "step" variable takes 0 before the intervention and 1 from the intervention.
- Another form of permanent effect is a change of slope. A trend that bends at the time of intervention and hence is non linear.


#### Trading days
- The number of trading days in a month can have a substantial effect on sales data.


#### Distributed lags
- The effect of advertising last beyond the actual campaign.
- Include lagged values of advertising expenditure.


#### Easter

#### Fourier series
- Alternative to using seasonal dummy variable
- Need fewer predictors than with dummy variable

```{r}
fourier_beer <- recent_production %>%
  model(TSLM(Beer ~ trend() + fourier(K = 2)))

report(fourier_beer)

```
