---
title: "7.5 Selecting predictors"
output: html_document
date: '2022-04-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp3)
```

#### Ex-ante versus ex-post forecasts
- Ex-ante forecast
  - Use only the information available in advance
- Ex-post forecast
  - Use actual observations of the predictors

#### Example: Australian quarterly beer production

- We know some predictors in advance 
  - Seasonal dummy variable
  - Public holiday indicator
  - Time trend

```{r}
recent_production <- aus_production %>%
  filter(year(Quarter) >= 1992)
fit_beer <- recent_production %>%
  model(TSLM(Beer ~ trend() + season()))
fc_beer <- forecast(fit_beer)
fc_beer %>%
  autoplot(recent_production) +
  labs(
    title = "Forecasts of beer production using regression",
    y = "megalitres"
  )
```

#### Scenario based forecasting

```{r}
fit_consBest <- us_change %>%
  model(
    lm = TSLM(Consumption ~ Income + Savings + Unemployment)
  )
future_scenarios <- scenarios(
  Increase = new_data(us_change, 4) %>%
    mutate(Income=1, Savings=0.5, Unemployment=0),
  Decrease = new_data(us_change, 4) %>%
    mutate(Income=-1, Savings=-0.5, Unemployment=0),
  names_to = "Scenario")

fc <- forecast(fit_consBest, new_data = future_scenarios)

us_change %>%
  autoplot(Consumption) +
  autolayer(fc) +
  labs(title = "US consumption", y = "% change")
```


#### Building a predictive regression model

- Use lagged values for regression model
- The predictor set is formed by values of the x that are abserved h time periods prior to observing y.

$$
y_{y+h} = \beta_0 + \beta_1x_{1,t} + \dots+\beta_kx_{k,t} +\varepsilon_{t+h}
$$

#### Prediction intervals

- Prediction interval for simple linear regression

$$
\hat{y} \pm 1.96\hat{\sigma_e}\sqrt{ 1 + \frac{1}{T}+\frac{(x-\bar{x})^2}{(T-1)s_x^2}}
$$

- Prediction interval is wider when x is apart from x_bar


```{r}
fit_cons <- us_change %>%
  model(TSLM(Consumption ~ Income))
new_cons <- scenarios(
  "Average increase" = new_data(us_change, 4) %>%
    mutate(Income = mean(us_change$Income)),
  "Extreme increase" = new_data(us_change, 4) %>%
    mutate(Income = 12),
  names_to = "Scenario"
)

fcast <- forecast(fit_cons, new_cons)

us_change %>%
  autoplot(Consumption) +
  autolayer(fcast) +
  labs(title = "US consumption", y = "% change")
```
